Getting started with dispRity

### 2020-08-19 inst/gitbook/02_getting-started.Rmd

## Ordinating the example data from Claddis
Claddis.ordination(Michaux1989) 
```

Note that several options are available, namely which type of distance should be computed.
See more info in the function manual (`?Claddis.ordination`).
Alternatively, it is of course also possible to manual calculate the ordination matrix using the functions `Claddis::MorphDistMatrix` and `stats::cmdscale`.

>>>>

## Ordinating the example data from Claddis
Claddis.ordination(michaux_1989)
```

Note that several options are available, namely which type of distance should be computed.
See more info in the function manual (`?Claddis.ordination`).
Alternatively, it is of course also possible to manual calculate the ordination matrix using the functions `Claddis::calculate_morphological_distances` and `stats::cmdscale`.
